\sysfull

### 2018-04-16 paper/hwswsetup.tex
Methodology details added in section 9

We used two platforms to evaluate \sys: (1) an \emph{intermittently-powered}
energy-harvesting device, and (2) a \emph{continuously-powered} evaluation
board.
%
Every benchmark listed in the next section was run repeatedly for X\,s on
each platform and the result was averaged for the duration of the experiment.
\todo{check if this is correct}{Carlo}

Experiments on the intermittently-powered platform used the
WISP\,5.1~\cite{wisp5,wisp} RF-powered energy-harvesting device.
%
The WISP contains the MSP430FR5969~\cite{wolverine} MCU with 64\,kB of
non-volatile (FRAM) memory and 2\,kB of volatile (SRAM) memory and was
configured to 1\,MHz clock speed.
%
We powered the WISP using an RF signal generator~\cite{} \todo{Add reference
to signal generator}{Przemek} emitting 20\,dBm sinusoidal wave at 915\,MHz.
The signal generator was connected to the Liard RFMAX S9028PCRJ 8\,dBic
antenna~\cite{atlas2015}.
%
The antenna was oriented towards and in parallel with the WISP antenna, and
no objects obstructed the path.
%
We affixed the WISP with a paper harness at the edge of a table, so that the
WISP was parallel to the table surface at a height of 10~cm.
%
For distance-controlled experiments we positioned the signal generator
antenna at a fixed distance from the WISP. The distances were $d=\{15, 30,
50\}$\,cm for the main experiments and 60~cm for the task downscaling
experiments.
%
To obtain execution time, the software toggled GPIO pins at the beginning and
end of the application, and the Saleae~\cite{saleae} logic analyzer measured
the interval between edges in the signal.

@@

We evaluated \sys using six benchmarks summarized in
Table~\ref{table:benchmark_table}. %
Three benchmarks (\textbf{ar}, \textbf{bc}, \textbf{cuckoo}) are from prior
work~\cite{chain,alpaca} and three benchmarks (\textbf{dijkstra},
\textbf{fft}, \textbf{sort}) are new implementations of applications
from the MiBench suite~\cite{mibench,hicks_mibench2_2016}. The
\textbf{fft} implementation is based on the Accelerated FFT library from
TI~\cite{ti-fft}.
%
\todo{add reference}{Przemek}
%
All applications were compiled using TI GCC~\cite{ti-gcc} version 3.8.0 with
\texttt{-O1}.
%
\todo{Check if this still holds. provide optimization flag}{Przemek} 
%
The source code for all benchmarks is released at \cite{coala_website}.

>>>>

We used two platforms to evaluate \sys: (1) an \emph{intermittently-powered}
energy-harvesting device, and (2) a \emph{continuously-powered} evaluation
board.
%
Every benchmark listed in the next section was run repeatedly on
each platform for a more or less long time window, depending on the benchmark,
to capture a diverse power trace and produce a high number of complete runs of all applications.
The results were averaged across the duration of the experiment.

Experiments on the intermittently-powered platform used the
WISP\,5.1~\cite{wisp5,wisp} RF-powered energy-harvesting device.
%
The WISP contains the MSP430FR5969~\cite{wolverine} MCU with 64\,kB of
non-volatile (FRAM) memory and 2\,kB of volatile (SRAM) memory and was
configured to 1\,MHz clock speed.
%
We powered the WISP using an RF signal generator~\cite{} \todo{Add reference
to signal generator}{Przemek} emitting  a 20-\,dBm sinusoidal wave at 915\,MHz.
The signal generator was connected to the Liard RFMAX S9028PCRJ 8\,dBic
antenna~\cite{atlas2015}.
%
The antenna was oriented towards and in parallel with the WISP antenna, and
no objects obstructed the path.
%
We affixed the WISP with a paper harness at the edge of a table, so that the
WISP was parallel to the table surface at a height of 10~cm.
%
For distance-controlled experiments we positioned the signal generator
antenna at a fixed distance from the WISP. The distances were $d=\{15, 30,
50\}$\,cm for the main experiments and 60~cm for the task downscaling
experiments.
%
To obtain execution time, the software toggled GPIO pins at sections of the code
under profile, and the Saleae~\cite{saleae} logic analyzer measured
the interval between edges in the signal.

@@

We evaluated \sys using six benchmarks summarized in
Table~\ref{table:benchmark_table}. %
Three benchmarks (\textbf{ar}, \textbf{bc}, \textbf{cuckoo}) are from prior
work~\cite{chain,alpaca} and three benchmarks (\textbf{dijkstra},
\textbf{fft}, \textbf{sort}) are new implementations of applications
from the MiBench suite~\cite{mibench,hicks_mibench2_2016}. The
\textbf{fft} implementation is based on the Accelerated FFT library from
TI~\cite{ti-fft}.
%
\todo{add reference}{Przemek}
%
All applications were compiled using MSP430 GCC~\cite{ti-gcc} version 6.4.0 with
\texttt{-O1} as optimization flag.
%
The source code for all benchmarks will be released at \cite{coala_website}.
